Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-28 doc/main_jfm.tex
still working on results sections

\todo[inline]{Bryan left off here}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Shear Flow}

Figure~\ref{figure9} demonstrates the simulation results of two
Janus-vesicles in a shear flow where the testing shear rate is
$\chi=0.005$ and the flow is given by $\dot x = \chi y$. In panel (a),
the starting frame, two center-of-mass positions are placed on the same
horizontal level, at $(-10,0)$ and $(10,0)$. Since we already have a
pre-relaxed $58$-body in previous sections, we duplicate the state to
have the initial configuration (shown in panel (a)) in this section. In
all panels, the blue and red curves represent the moving paths of two
Janus-vesicle centroids and they move nearly a round when $t=4000$ as
shown in panel (h). We observe that the rotation continues as time goes
and an interesting event occurs in the simulation that an adhesive
effect can be seen and tuned. In other words, the adhesive behavior will
be absent when two vesicles are centered at a different level and are
well separated in $y$-direction.

The fluid pressure profiles of snapshots are given in
Figure~\ref{figure10}. As expected, there is no pressure jump between
the internal and external fluids from the beginning of the simulation
and this is shown in the background pressure plot. Panels (b)-(d) show
the configurations when $t = \{500,1000,1500\}$ and the streamlines are
plotted in the background for all panels. We include the numerical
results using a continuum model in all insets and these comparisons give
a qualitative agreement between two models.

%\todo[inline]{Migration pattern and/or separation distance. See Fig 8 in
%JCP paper by Rahimian, Veerapaneni, and Biros.}

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
\end{center} 
  \caption{Trajectories of different setups in two-vesicle in an extensional flow and the moving paths of two centroids of two Janus-vesicles are plotted in blue and red. (i) Both centroids of two Janus-vesicles are on the $x$-axis; (ii) The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis; (iii) 
  The centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure12} presents the numerical results from the case (iii) and a 
  consistent flow rate is $\chi = 0.005$ for all cases.}
    \label{figure11}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{N116_ext_0.pdf}
\includegraphics[height=2in]{N116_ext_2000.pdf}\\
\includegraphics[height=2in]{N116_ext_4000.pdf}
\includegraphics[height=2in]{N116_ext_6500.pdf}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\chi=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple. The insets show the results produced from using continuum model that the streamlines have perfect agreements with the present results.
  }
    \label{figure12}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Shear Flow}

Figure~\ref{figure9} shows the simulation of two Janus-vesicles in a
shear flow with shear rate $\chi=0.005$. Using the pre-relaxed $58$-body
Janus-vesicle in previous sections, we duplicate the state to have the
initial configuration shown in panel (a). The two centers of mass are at
$(-10,0)$ and $(10,0)$. In all panels, the blue and red curves show the
trajectory of the two Janus-vesicle centroids. They have nearly
completed a full period by $t=4000$ as shown in panel (h). We also
observe an adhesive effect between the two Janus-vesicles that is set up
by the hydrophobic interactions and repulsive force. Similar dynamics
have been observed between a pair of adhering vesicles in a shear flow
(\cite{qua-vee-you2019, abb-far-ezz-ben-mis2021}). This adhesive
behavior is absent when two Janus-vesicles are well-separated.

The fluid pressure profiles snapshots are given in
Figure~\ref{figure10}. Since the initial Janus-vesicles are pre-relaxed,
there is initially no pressure jump between the internal and external
fluids (panel (a)). Panels (b)--(d) show the configurations when $t =
\{500,1000,1500\}$ and the streamlines are plotted in the background for
all panels. We include the numerical results using a continuum model in
all insets and these comparisons give a qualitative agreement between
two models.

\todo[inline]{Bryan left off here}
\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
\end{center} 
  \caption{\label{figure11} Trajectories of different setups in
  two-vesicle in an extensional flow and the moving paths of two
  centroids of two Janus-vesicles are plotted in blue and red. (i) Both
  centroids of two Janus-vesicles are on the $x$-axis; (ii) The centroid
  of the left Janus-vesicle is $0.1$ unit above the $x$-axis; (iii) The
  centroid of the left Janus-vesicle is $0.1$ unit above the $x$-axis
  and the other one is $0.1$ unit below the $x$-axis; (iv) The centroid
  of the left Janus-vesicle is $0.5$ unit above the $x$-axis and the
  other one is $0.5$ unit below the $x$-axis; Figure~\ref{figure12}
  presents the numerical results from the case (iii) and a consistent
  flow rate is $\chi = 0.005$ for all cases.}
\end{figure}

\begin{figure}
\centering
\includegraphics[height=2in]{N116_ext_0.pdf}
\includegraphics[height=2in]{N116_ext_2000.pdf}\\
\includegraphics[height=2in]{N116_ext_4000.pdf}
\includegraphics[height=2in]{N116_ext_6500.pdf}
  \caption{\label{figure12} Two vesicles under an extensional flow where
  the dimensioneless shear rate is $\chi=0.005$; The initial
  configuration is shown in panel (a). The background color indicates
  the magnitude of fluid pressure. From dark red to dark blue, it
  represents the pressure varies from high to low values. The color bar
  is valid for all panels. Streamlines are plotted in purple. The insets
  show the results produced from using continuum model that the
  streamlines have perfect agreements with the present results.}
\end{figure}
